Comparison of Catalogs

### 2024-10-19 compare/compare.tex
minor fixes

In this script we will compare 2 catalogs, HECATE (Kovlakas et al.
(2021)) and LCV (Karachentsev and Kaisina (2013))

@@

The dataset we are going to use for the comparison (inner join) consists
of 288 galaxies and 168 columns.

@@

\subsection{Completeness of the LCV
Catalog}\label{completeness-of-the-lcv-catalog}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Radial velocities of
  \begin{equation}\phantomsection\label{eq-lcv-vel}{
   V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
  }\end{equation}
\item
  Distances of \begin{equation}\phantomsection\label{eq-lcv-dis}{
     D<11\ \text{Mpc}
     }\end{equation}
\end{enumerate}

@@

  \begin{itemize}
  \tightlist
  \item
    Accurate distances are mainly known within \textasciitilde5 Mpc.
  \item
    Non-Hubble motions (\textasciitilde300 km/s)\footnote{\emph{Non-Hubble
      motion refers to the component of a galaxy's velocity that
      deviates from the uniform expansion of the universe, described by
      the equation} \(V= H_0 d + v_p\),where \(V\) is the total
      velocity, \(H_0 d\) represents the Hubble flow, and
      \(v_p\)\hspace{0pt} is the peculiar velocity. {``Essay''} (n.d.)}
    may make up half of the adopted velocity constraint
    (Equation~\ref{eq-lcv-vel})
  \item
    Solution for our usage: only keep the galaxies inside a radius of
    \(D=11 Mpc\)
  \item
    HI sources in surveys with low angular resolution: ``The presence
    around our Galaxy of hundreds of high-velocity clouds with low
    line-of-sight velocities and small W50 widths also provokes the
    inclusion of false ``nearby'' dwarf galaxies in the
    LV''(Karachentsev, Makarov, and Kaisina (2013))
  \end{itemize}
\item
  Astro-Spam and Survey Errors: - Automatic surveys produce false
  detections (e.g., stars misclassified as galaxies, high-velocity
  clouds mistaken for dwarfs).
\item
  Conditional Completeness Estimate: - Galaxies brighter than
  \(M_B^c = -11^m\) or with linear diameters larger than
  \(A_{26} = 1.0\) kpc show (40--60)\% completeness. - ``among the
  members of the Local Group (D \textless{} 1 Mpc), only half of the
  galaxies have absolute magnitudes brighter than −11m. Consequently,
  more than half of the ultra-faint dwarf companions around normal
  galaxies, like the Sombrero galaxy (D = 9.3 Mpc), still remain outside
  our field of view.''
\item
  Undetected Ultra-Faint Dwarfs: - Many faint dwarf galaxies remain
  undetected beyond the Local Group. Estimated population of undetected
  dwarfs could be as large as \(10^3–10^4\) within the LV.
\item
  Surface Brightness Distribution: - Surface brightness remains
  consistent across distances, except for ultra-faint dwarfs
  (\(SB <31 \text{mag}\cdot\text{arcsec}^{-2}\)). - Faintest dwarf
  galaxies are detectable only nearby due to their resolution into
  individual stars.
\item
  Luminosity-Size Relationship: - Observations align with cosmological
  models predicting \(L\sim A^3\) (Navarro, Frenk, and White (1996)),
  though deviations occur for extremely low surface brightness galaxies.
  - ``The deviation from it at the extremely low surface brightness end
  is due to a systematic overestimation of dwarf galaxy sizes, the
  brightness profiles of which lie entirely below the Holmberg
  isophote.''
\end{enumerate}

@@

\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
Table & Number of galaxies \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Inner join & 288 \\
Outer join & 2901 \\
LCV & 1316 \\
HECATE & 2901 \\
Unique galaxies in LCV & 1028 \\
Unique Galaxies in Hecate & 2613 \\
\end{longtable}

@@

Completeness (LCV)= 22 \%

@@

Completeness (LCV)= 78 \%

Combined Completeness
=\(\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LCV}}\)=
80 \%

@@

\subcaption{\label{fig-dis-comp-2}LCV}

@@

\subcaption{\label{fig-type-comp-2}LCV}

@@

As we can see from the histograms (Figure~\ref{fig-dis-comp}) and
(Figure~\ref{fig-type-comp}) the sample of unique galaxies of each
catalog, gets smaller by an almost constant proportion (Inner join).

This means there is no bias in the selection of the galaxies.

@@

\[\text{Percentage change} = \frac{V_{Hecate} - V_{LCV}}{V_{Hecate}}\cdot 100 \%\]

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2329}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3014}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pearson Correlation {[}-1,1{]}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Dis & D & Distance & 0.881 \\
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Linear Correlation
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
RVel (km/s) & V (km/s) & Heliocentric radial velocity & 0.994 \\
VLG (km/s) & & Radial velocity & \\
cz (km/s) & & Heliocentric velocity & \\
& V\_VIR (km/s) & Virgo-infall corrected radial velocity & \\
\end{longtable}

@@

\caption{\label{fig-vel-pairplot}The correlation Matrix of the
Velocities. The lower left triangle is is composed of the scatter plots
of the various velocities, the diagonal shows their distrubution and the
upper right triangle shows the correlations of the Velocities}

@@

{[}?{]} The close correlation between all of the velocities, could be
due to the fact that all of them measure the velocity of each galaxy,
but from a different frame of reference.

The strong correlation between the velocities reported by the HECATE and
LCV catalogs can be attributed to the fact that both measure the same
intrinsic galaxy velocities but reference them to different frames. For
instance, velocities can be corrected for the movement of the Earth
(heliocentric frame) or the for the Virgo-infall. These corrections
shift the measured velocity slightly, but the fundamental measurement
remains consistent. This explains why the velocities are highly
correlated, as they represent the same physical phenomenon but adjusted
for different reference points.

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pearson Correlation {[}-1,1{]}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
TType & T (with errors) & Numerical Hubble type following the de
Vaucouleurs system & 0.7107 \\
inc & INCL & Inclination (deg) & 0 \\
a26\_1 (Major) & R1 (Semi-major axis) & angular diameter (arcmin) & 0 \\
\end{longtable}

@@

@@

\subcaption{\label{fig-types-compare-2}Comparison with the correction
\(|{T_{HECATE}-T_{LCV}}|<7\)}

@@

\begin{itemize}
\tightlist
\item
  we can assume that the galaxies from the upper left and lower right
  regions of the plot are classified differently because of this
\item
  this might explain the large errors E\_T of HECATE
\item
  why we see a difference in the distribution of
  (Figure~\ref{fig-type-comp})
\end{itemize}

We can remove the ``problematic'' galaxies by only keeping the ones
with: \[
|{T_{HECATE}-T_{LCV}}|<\sigma_{T_{LCV}} = 4.8
\]

\begin{itemize}
\tightlist
\item
  The average uncertainty of the morphological type in the HECATE
  catalog is \(\overline{\delta T} = \pm 1.4\), so the intercept is
  included in the error.
\item
  So we can assume that the Distances are the same
\end{itemize}

@@

\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
& inc & INCL & Percentage Change {[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 287 & 209 & 202 \\
mean & 60 & 59 & -0 \\
std & 19 & 23 & 0 \\
min & 9 & 0 & -3 \\
25\% & 47 & 47 & -0 \\
50\% & 60 & 59 & 0 \\
75\% & 72 & 78 & 0 \\
max & 90 & 90 & 1 \\
\end{longtable}

We can see that for values in the range
\([\sim 30^\circ,\sim 80^\circ]\), the values of the LCV inclination are
higher (Figure~\ref{fig-incl-compare}). However, since their means,
median, min and maxes are similar and the percentage change is
practically 0\% (mean, median, \(\sigma\) = 0 with a range
\([-3\%,1\%]\)), we can ignore the differences and assume they are the
same values.

@@

\begin{longtable}[]{@{}cccc@{}}
\toprule\noalign{}
LCV & HECATE & Description & Pearson Correlation {[}-1,1{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
logKLum & logL\_K & & 0 \\
\end{longtable}

@@

\[
\log(L_{K,HEC})=1.16\log(L_{K,LCV})-1.78=\log\left(\frac{{L_{K,LCV}}^{1.16}}{10^{1.78}}\right) \Leftrightarrow L_{K,HEC}=0.02\cdot{L_{K,LCV}}^{1.16}
\]

To assess whether the two galaxy catalogs have a 1-1 correlation, I
applied two types of linear fits to the data: a free fit and a forced
fit. The free fit allows both the slope and intercept to vary freely,
meaning the line can take on any slope and can cross the y-axis at any
point. In contrast, for the forced fit, I set the slope to exactly 1 and
fixed the line to pass through the origin, meaning the equation becomes
y=xy=x. This forced fit represents a perfect 1-1 relationship, where the
values from one catalog should match the other exactly, without any
shift or scaling.

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pearson Correlation {[}-1,1{]}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
mag\_B (with errors) & BT (with errors) & & 0 \\
Kmag & K & 2MASS band magnitude (both) & 0 \\
\end{longtable}

@@

\includegraphics{compare_files/figure-pdf/cell-26-output-1.pdf}

\includegraphics{compare_files/figure-pdf/cell-26-output-2.pdf}

\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
& Percentage Change {[}\%{]} & Percentage Change, after 3 sigma clip
{[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 70 & 70 \\
mean & -5 & -5 \\
std & 12 & 10 \\
min & -70 & -42 \\
50\% & -0 & -0 \\
max & 16 & 16 \\
\end{longtable}

{[}?{]} this 5\% mean in the difference probably exists because of the
low number of galaxies we compare, so we can ignore it.

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2603}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2466}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Count
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
& logSFR\_TIR & Decimal logarithm of the total-infrared SFR estimate
{[}Msol/yr{]} & 21 \\
& logSFR\_FIR & Decimal logarithm of the far-infrared SFR estimate
{[}Msol/yr{]} & 22 \\
& logSFR\_60u & Decimal logarithm of the 60um SFR estimate {[}Msol/yr{]}
& 48 \\
& logSFR\_12u & Decimal logarithm of the 12um SFR estimate {[}Msol/yr{]}
& 26 \\
& logSFR\_22u & Decimal logarithm of the 22um SFR estimate {[}Msol/yr{]}
& 23 \\
& logSFR\_HEC & Decimal logarithm of the homogenised SFR estimate
{[}Msol/yr{]} & 73 \\
& logSFR\_GSW & Decimal logarithm of the SFR in GSWLC-2 {[}Msol/yr{]} &
0 \\
SFRFUV & & FUV derived integral star formation rate & 220 \\
SFRHa & & H\{alpha\} derived integral star formation rate & 223 \\
\end{longtable}

\includegraphics{compare_files/figure-pdf/cell-29-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/fig-sfr-lcv-output-1.pdf}

@@

\subcaption{\label{fig-sfr-lcv-1}Linear scale}

@@

\includegraphics{compare_files/figure-pdf/fig-sfr-lcv-output-2.pdf}

@@

\subcaption{\label{fig-sfr-lcv-2}Decimal logarithmic scale}

@@

\caption{\label{fig-sfr-lcv}Comparison of the \(SFR_{FUV}-SFR_{Ha}\) of
the galaxies}

@@

The SFR according to (Kroupa et al. (2020)), can be calculated from the
mean of SFR from the Ha and FUV, for \(SFR>10^{-3}\ M_\odot\, yr^{-1}\).
As we can see from the plots (Figure~\ref{fig-sfr-lcv}) it is a good
aproximation for all SFR's

\[
SFR = \frac{SFR_{FUV}+SFR_{H\alpha}}{2}, \text{if both exist, else: } SFR = SFR_i,\ i= FUV,\, H\alpha
\]

@@

{[}?{]}EXPLANATION this low correlation maybe comes from the
inaccuracy/approximation of (Kroupa et al. (2020))

The reason is that this aproximation is accurate if we consider a stable
SFR over time. However, we tend to observe higher Ha for more recent SF
activity. (we discussed it in our last meeting, I need a refrence).

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LCV
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Count
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
logM26 & & Log mass within Holmberg radius & 233 \\
logMHI & & Log mass within Holmberg radius & 233 \\
& logM\_HEC & Decimal logarithm of the stellar mass {[}Msol{]} & 64 \\
& logM\_GSW & Decimal logarithm of the stellar mass in GSWLC-2
{[}Msol{]} & 0 \\
logStellarMass & & Stellar Mass from \(M_*/L=0.6\) & 287 \\
\end{longtable}

>>>>

In this script we will compare 2 catalogs, HECATE (Kovlakas et al.
(2021)) and LVG (Karachentsev and Kaisina (2013))

@@

The dataset we are going to use for the comparison (inner join) consists
of 288 galaxies and 168 columns with their physical characteristics.

@@

\subsection{Completeness of the LVG
Catalog}\label{completeness-of-the-lvg-catalog}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Radial velocities of
\end{enumerate}

\begin{equation}\phantomsection\label{eq-lvg-vel}{
     V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
}\end{equation}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Distances of
\end{enumerate}

\begin{equation}\phantomsection\label{eq-lvg-dis}{
       D<11\ \text{Mpc}
}\end{equation}

@@

  \begin{itemize}
  \tightlist
  \item
    Accurate distances are mainly known within \textasciitilde5 Mpc.
  \item
    Non-Hubble motions (\textasciitilde300 km/s)\footnote{\emph{Non-Hubble
      motion refers to the component of a galaxy's velocity that
      deviates from the uniform expansion of the universe, described by
      the equation} \(V= H_0 d + v_p\),where \(V\) is the total
      velocity, \(H_0 d\) represents the Hubble flow, and
      \(v_p\)\hspace{0pt} is the peculiar velocity. {``Essay''} (n.d.)}
    may make up half of the adopted velocity constraint
    (Equation~\ref{eq-lvg-vel})

    \begin{itemize}
    \tightlist
    \item
      Solution for our usage: only keep the galaxies inside a radius of
      \(D=11 Mpc\)
    \end{itemize}
  \item
    HI sources in surveys with low angular resolution: ``The presence
    around our Galaxy of hundreds of high-velocity clouds with low
    line-of-sight velocities and small W50 widths also provokes the
    inclusion of false ``nearby'' dwarf galaxies in the
    LV''(Karachentsev, Makarov, and Kaisina (2013))
  \end{itemize}
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Astro-Spam and Survey Errors:

  \begin{itemize}
  \tightlist
  \item
    Automatic surveys produce false detections (e.g., stars
    misclassified as galaxies, high-velocity clouds mistaken for
    dwarfs).
  \end{itemize}
\item
  Conditional Completeness Estimate: - Galaxies brighter than
  \(M_B^c = -11^m\) or with linear diameters larger than
  \(A_{26} = 1.0\) kpc show (40--60)\% completeness.

  \begin{itemize}
  \tightlist
  \item
    ``among the members of the Local Group (D \textless{} 1 Mpc), only
    half of the galaxies have absolute magnitudes brighter than
    \(−11^m\). Consequently, more than half of the ultra-faint dwarf
    companions around normal galaxies, like the Sombrero galaxy (D = 9.3
    Mpc), still remain outside our field of view.''
  \end{itemize}
\item
  Undetected Ultra-Faint Dwarfs:

  \begin{itemize}
  \tightlist
  \item
    Many faint dwarf galaxies remain undetected beyond the Local Group.
    Estimated population of undetected dwarfs could be as large as
    \(10^3–10^4\) within the LV.
  \end{itemize}
\item
  Surface Brightness Distribution:

  \begin{itemize}
  \tightlist
  \item
    Surface brightness remains consistent across distances, except for
    ultra-faint dwarfs (\(SB <31 \text{mag}\cdot\text{arcsec}^{-2}\)).
  \item
    Faintest dwarf galaxies are detectable only nearby due to their
    resolution into individual stars.
  \end{itemize}
\item
  Luminosity-Size Relationship:

  \begin{itemize}
  \tightlist
  \item
    Observations align with cosmological models predicting \(L\sim A^3\)
    (Navarro, Frenk, and White (1996)), though deviations occur for
    extremely low surface brightness galaxies.
  \item
    ``The deviation from it at the extremely low surface brightness end
    is due to a systematic overestimation of dwarf galaxy sizes, the
    brightness profiles of which lie entirely below the Holmberg
    isophote.''
  \end{itemize}
\end{enumerate}

@@

\begin{longtable}[]{@{}lr@{}}
\toprule\noalign{}
Table & Number of galaxies \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Inner join & 288 \\
Outer join & 2901 \\
LVG & 1316 \\
HECATE & 2901 \\
Unique galaxies in LVG & 1028 \\
Unique Galaxies in Hecate & 2613 \\
\end{longtable}

@@

Completeness (LVG)= 22 \%

@@

Completeness (LVG)= 78 \%

Combined Completeness
=\(\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LVG}}\)=
80 \%

@@

\subcaption{\label{fig-dis-comp-2}LVG}

@@

\subcaption{\label{fig-type-comp-2}LVG}

@@

@@

\[\text{Percentage change} = \frac{V_{Hecate} - V_{LVG}}{V_{Hecate}}\cdot 100 \%\]

@@

\begin{longtable}[]{@{}ccc@{}}
\toprule\noalign{}
LVG & HECATE & Description \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Dis & D & Distance \\
\end{longtable}

@@

\begin{longtable}[]{@{}ccc@{}}
\toprule\noalign{}
LVG & HECATE & Description \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
RVel (km/s) & V (km/s) & Heliocentric radial velocity \\
VLG (km/s) & & Radial velocity \\
cz (km/s) & & Heliocentric velocity \\
& V\_VIR (km/s) & Virgo-infall corrected radial velocity \\
\end{longtable}

@@

\caption{\label{fig-vel-pairplot}The correlation Matrix of the
Velocities. The lower left triangle is composed of the scatter plots of
the various velocities, the diagonal shows their distrubution and the
upper right triangle shows the correlations of the Velocities}

@@

{[}?{]} The strong correlation between the velocities reported by the
HECATE and LVG catalogs (Figure~\ref{fig-vel-pairplot}) can be
attributed to the fact that both measure the same intrinsic galaxy
velocities but reference them to different frames. For instance,
velocities can be corrected for the movement of the Earth (heliocentric
frame) or the for the Virgo-infall. These corrections shift the measured
velocity slightly, but the fundamental measurement remains consistent.
This explains why the velocities are highly correlated, as they
represent the same physical phenomenon but adjusted for different
reference points.

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3273}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3273}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3455}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LVG
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
TType & T (with errors) & Numerical Hubble type following the de
Vaucouleurs system \\
inc & INCL & Inclination (deg) \\
a26\_1 (Major) & R1 (Semi-major axis) & angular diameter (arcmin) \\
\end{longtable}

@@

``as they correspond to types T \textless{} 1. The shortcomings of such
a simplified classification of dwarf systems have become apparent;
hence, van den Bergh (1959) proposed a more refined scheme where dwarf
galaxies were assumed to be divided by luminosity class\ldots Such an
approach allowed us to avoid unpleasant cases in which a dwarf galaxy of
intermediate type jumps over due to a misclassification from one end of
the de Vaucouleurs sequence (T \textless{} 1) to the other (T = 9,
10).'' (Karachentsev and Kaisina (2013))

@@

\subcaption{\label{fig-types-compare-2}Comparison with the correction
\(|{T_{HECATE}-T_{LVG}}|<σ_{Τ_{LVG}}\)}

@@

\begin{itemize}
\tightlist
\item
  we can assume that the galaxies from the upper left and lower right
  regions of the plot are classified differently because of this
\item
  this might explain the large errors \(\delta T\) of HECATE
\item
  why we see a difference in the distribution of
  (Figure~\ref{fig-type-comp})
\end{itemize}

We can remove the ``problematic'' galaxies by only keeping the ones
with: \[
|{T_{HECATE}-T_{LVG}}|<\sigma_{T_{LVG}} = 4.8
\]

\begin{itemize}
\tightlist
\item
  The average uncertainty of the morphological type in the HECATE
  catalog is \(\overline{\delta T} = \pm 1.4\), so the intercept is
  included in the error.
\item
  So we can assume that the Morphological Types are the same
\end{itemize}

@@

\begin{longtable}[]{@{}llll@{}}
\toprule\noalign{}
& inc & INCL & Percentage Change {[}\%{]} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
count & 287 & 209 & 202 \\
mean & 60 & 59 & -0 \\
std & 19 & 23 & 0 \\
min & 9 & 0 & -3 \\
50\% & 60 & 59 & 0 \\
max & 90 & 90 & 1 \\
\end{longtable}

We can see that for values in the range
\([\sim 30^\circ,\sim 80^\circ]\), the values of the LVG inclination are
higher (Figure~\ref{fig-incl-compare}). However, since their means,
median, min and maxes are similar and the percentage change is
practically 0\% (mean, median, \(\sigma\) = 0 with a range
\([-3\%,1\%]\)), we can ignore the differences and assume they are the
same values.

@@

\begin{longtable}[]{@{}ccc@{}}
\toprule\noalign{}
LVG & HECATE & Description \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
logKLum & logL\_K & \\
\end{longtable}

@@

\[
\log(L_{K,HEC})=1.16\log(L_{K,LVG})-1.78=\log\left(\frac{{L_{K,LVG}}^{1.16}}{10^{1.78}}\right) \Leftrightarrow L_{K,HEC}=0.02\cdot{L_{K,LVG}}^{1.16}
\]

To assess whether the two galaxy catalogs have a 1-1 correlation, I
applied two types of linear fits to the data: a free fit and a forced
fit. The free fit allows both the slope and intercept to vary freely,
meaning the line can take on any slope and can cross the y-axis at any
point. In contrast, for the forced fit, I set the slope to exactly 1 and
fixed the line to pass through the origin, meaning the equation becomes
\(y=x\). This forced fit represents a perfect 1-1 relationship, where
the values from one catalog should match the other exactly, without any
shift or scaling.

@@

\begin{longtable}[]{@{}ccc@{}}
\toprule\noalign{}
LVG & HECATE & Description \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
mag\_B (with errors) & BT (with errors) & \\
Kmag & K & 2MASS band magnitude (both) \\
\end{longtable}

@@

@@

\includegraphics{compare_files/figure-pdf/fig-kmag-compare-output-1.pdf}

@@

\subcaption{\label{fig-kmag-compare-1}Linear Regression with free
paramaters, \(y=ax+b\)}

@@

\includegraphics{compare_files/figure-pdf/fig-kmag-compare-output-2.pdf}

@@

\subcaption{\label{fig-kmag-compare-2}Linear Regrassion \(y=x\)}

@@

\caption{\label{fig-kmag-compare}Comparison of the \(L_K\) of the
galaxies.}

@@

Following the same logic as in Figure~\ref{fig-klum-compare}, we force
the parameters of the linear regression to be \(y=1\cdot x + 0\).

In this case, the data is such that both the forced fit and the free fit
explain the variance almost identically
(Figure~\ref{fig-kmag-compare-2}). This can happen when the data roughly
follows the pattern \(y≈x\), but with a slight bias that the free fit
can account for (in this case, a slope slightly greater than 1 and a
negative intercept).

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3273}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3273}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3455}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LVG
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
& logSFR\_TIR & Decimal logarithm of the total-infrared SFR estimate
{[}Msol/yr{]} \\
& logSFR\_FIR & Decimal logarithm of the far-infrared SFR estimate
{[}Msol/yr{]} \\
& logSFR\_60u & Decimal logarithm of the 60um SFR estimate
{[}Msol/yr{]} \\
& logSFR\_12u & Decimal logarithm of the 12um SFR estimate
{[}Msol/yr{]} \\
& logSFR\_22u & Decimal logarithm of the 22um SFR estimate
{[}Msol/yr{]} \\
& logSFR\_HEC & Decimal logarithm of the homogenised SFR estimate
{[}Msol/yr{]} \\
& logSFR\_GSW & Decimal logarithm of the SFR in GSWLC-2 {[}Msol/yr{]} \\
SFRFUV & & FUV derived integral star formation rate \\
SFRHa & & H\{alpha\} derived integral star formation rate \\
\end{longtable}

\includegraphics{compare_files/figure-pdf/fig-sfr-pairplot-output-1.pdf}

\caption{\label{fig-sfr-pairplot}Comparison of the \(SFR_{i}\) of the
galaxies}

The SFR according to (Kroupa et al. (2020)), can be calculated from the
mean of SFR from the Ha and FUV, for \(SFR>10^{-3}\ M_\odot\, yr^{-1}\).
As we can see from the plots (Figure~\ref{fig-sfr-lvg}) it could be a
good aproximation.

\begin{equation}\phantomsection\label{eq-sfr-mean}{
SFR = \frac{SFR_{FUV}+SFR_{H\alpha}}{2}, \text{if both exist, else: } SFR = SFR_i,\ i= FUV,\, H\alpha
}\end{equation}

\includegraphics{compare_files/figure-pdf/fig-sfr-lvg-output-1.pdf}

\subcaption{\label{fig-sfr-lvg-1}Linear scale}

\includegraphics{compare_files/figure-pdf/fig-sfr-lvg-output-2.pdf}

\subcaption{\label{fig-sfr-lvg-2}Decimal logarithmic scale}

\caption{\label{fig-sfr-lvg}Comparison of the \(SFR_{FUV}-SFR_{Ha}\) of
the galaxies}

@@

The low correlation in Figure~\ref{fig-sfr-compare-1} and the interval
in Figure~\ref{fig-sfr-compare-2} show that the approximation
(Equation~\ref{eq-sfr-mean}) is not great. According to Karachentsev and
Kaisina (2013):

\begin{itemize}
\item
  \textbf{Hα and FUV timescales}: \(H_\alpha\) traces short-term star
  formation (\textasciitilde10 Myr) via massive O-type stars, while FUV
  traces longer-term star formation (\textasciitilde100 Myr) from B-type
  stars.
\item
  \textbf{Discrepancies due to star formation bursts}: In galaxies with
  bursty or episodic star formation, Hα can significantly overestimate
  SFR compared to FUV, which lags in reflecting recent star formation
  events.
\item
  \textbf{Low-mass galaxy variability}: The scatter between
  \(SFR_{\text{H}\alpha}\) and \(SFR_{\text{FUV}}\) is particularly high
  in low-mass, dwarf galaxies, where stochastic star formation history
  causes wide variability between the two indicators.
\item
  \textbf{Measurement uncertainties}: Internal extinction, errors in
  distance estimates, and IMF stochasticity introduce biases in both Hα
  and FUV fluxes, making simple averaging inappropriate.
\item
  \textbf{Conclusion}: The
  \(SFR_{\text{total}} = \text{mean}(SFR_{\text{H}\alpha}, SFR_{\text{FUV}})\)
  method oversimplifies the complexity of star formation processes and
  is not reliable for galaxies with variable star formation or
  significant measurement uncertainties
\end{itemize}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
LVG
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
HECATE
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Description
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
logM26 & & Log mass within Holmberg radius \\
logMHI & & Log mass within Holmberg radius \\
& logM\_HEC & Decimal logarithm of the stellar mass {[}Msol{]} \\
& logM\_GSW & Decimal logarithm of the stellar mass in GSWLC-2
{[}Msol{]} \\
logStellarMass & & Stellar Mass from \(M_*/L=0.6\) \\
\end{longtable}
